Macroscopic Salt Rejection through Electrostatically Gated Porous Graphene

### 2019-01-14 paper/paper.tex
Add abstract from Shih

%%%%%%%%%%%%%%%%%%%%
%Main
%%%%%%%%%%%%%%%%%%%%
\begin{document}
\clearpage{}
\begin{abstract}
  {\normalsize Atomically thin porous graphene membranes are emerging
    as one of the most promising candidates as next-generation
    membrane technology owing to their unique transport physics and
    high permeation. Among the current challenges of 2D membranes is
    the understanding of fundamental ion transport as well as its
    control towards applications in ion rectification, ionic
    transistors or desalination.  Here we report the study of
    tailoring the ion transport through atomically-thin porous
    graphene with pore sizes of 20$\pm$10 nanometers, and a pore
    density of 1.25$\pm$0.25$\times$10$^{10}$ cm$^{-2}$. By
    electrostatically gating a sheet of porous graphene, we
    demonstrate a considerable reduction of salt flux by up to 55\%
    and 85\% using a gate voltage, based on our experiments and
    theoretical predictions, respectively. We systematically
    investigate the effects of salt concentration and species,
    including the development of a theory to model the electrolyte
    diffusion through a nanopore in a sheet of gated graphene. The
    interplay between graphene quantum capacitance and electrical
    double layer is identified to be the main mechanism responsible
    for the observed salt flux reduction, when the pore size is
    comparable to the Debye length. Our findings reveal a new degree
    of freedom controlling the membrane potential and electrolyte
    permeation through porous two-dimensional materials.  }
\end{abstract}

>>>>

%%%%%%%%%%%%%%%%%%%%
%Main
%%%%%%%%%%%%%%%%%%%%
\begin{document}
\clearpage{}
\begin{abstract}
  {\normalsize
    Atomically thin porous graphene membranes are emerging as one of
    the most promising candidates for the next-generation membrane
    technology owing to the ultrahigh permeation. However, the
    transport selectivity relies on the precise control over pore size
    and shape, considerably limiting the scalability. Here, we study
    electrolyte permeation through a sheet of large-area, porous
    graphene membrane, with relatively large pore sizes of 20$\pm$10
    nanometers. Counterintuitively, we observe macroscopic salt
    rejection by applying electrostatically gating, which reduces the
    diffusive flux by up to one order of magnitude. We systematically
    investigate the effects of salt concentration and species,
    including developing a theory to model the electrolyte diffusion
    through a nanopore in a sheet of gated graphene. The interplay
    between graphene quantum capacitance and the electrical double
    layer is found to selectively modulate the anionic and cationic
    transport paths, creating voltage-dependent electrochemical
    barriers when the pore size is comparable to the Debye length. Our
    findings reveal a new degree of freedom regulating electrolyte
    permeation through porous two-dimensional materials.

    % Atomically thin porous graphene membranes are emerging
    % as one of the most promising candidates as next-generation
    % membrane technology owing to their unique transport physics and
    % high permeation. Among the current challenges of 2D membranes is
    % the understanding of fundamental ion transport as well as its
    % control towards applications in ion rectification, ionic
    % transistors or desalination.  Here we report the study of
    % tailoring the ion transport through atomically-thin porous
    % graphene with pore sizes of 20$\pm$10 nanometers, and a pore
    % density of 1.25$\pm$0.25$\times$10$^{10}$ cm$^{-2}$. By
    % electrostatically gating a sheet of porous graphene, we
    % demonstrate a considerable reduction of salt flux by up to 55\%
    % and 85\% using a gate voltage, based on our experiments and
    % theoretical predictions, respectively. We systematically
    % investigate the effects of salt concentration and species,
    % including the development of a theory to model the electrolyte
    % diffusion through a nanopore in a sheet of gated graphene. The
    % interplay between graphene quantum capacitance and electrical
    % double layer is identified to be the main mechanism responsible
    % for the observed salt flux reduction, when the pore size is
    % comparable to the Debye length. Our findings reveal a new degree
    % of freedom controlling the membrane potential and electrolyte
    % permeation through porous two-dimensional materials.
  }
\end{abstract}
